\documentclass[a4paper, 9pt]{extarticle}

\input{packages.tex}
\input{style.tex}
\input{cvref.tex}

\begin{document}

\maketitle{}
\myeducation{}
\myexperience{}

\section{Capstone Project}

\subsection{Security Enhanced Messaging Platform (Python 3)} \hfill \\
\begin{itemize}
	\item Python Diffie-Hellman library
	\item MongoDB
	\item WebSocket
\end{itemize}

\section{Personal Projects}

\subsection{IBBApi CLI (C++)} \hfill \\
\begin{itemize}
	\item It connects several IBB (Istanbul Metropolitan Municipality) API's from cli.
	\item It's start as a project to get whosale market hall prices from IBB API to use
		with \underline{\emph{\hyperref[lisp:frp]{Food Recipe Package (ELisp)}}}.
\end{itemize}

\subsection{4DOF Ballistics Software (C++)} \hfill \\
\begin{itemize}
	\item Made for 4-DOF ballistic calculations.
	\item Also have windage values (but don't have windage corrections).
\end{itemize}


\subsection{Food Recipe Package (ELisp)} \label{lisp:frp} \hfill \\
\begin{itemize}
	\item Emacs package that reads food recipe files and change the ingredients
	values according to main value.
	\item Purpose of this package is that some food recipe ingredients has to be
	calculated according to main ingredient
	(e.g. Bread ingredients calculated according to flour). When you change your
	main ingredient value whole recipe ingredients values are changes according
	to it.
\end{itemize}


\subsection{Metric $\longleftrightarrow$ Imperial Convertor (ELisp)} \hfill \\
\begin{itemize}
	\item Emacs package that converts imperial units to metric units
	(and vice versa).
	\item Also can scan Emacs region and automaticaly converts units. If imperial
	unit can be converted to more than one metric unit (e.g. foot to cm or mm)
	use predefined rule to convert more suitable one.
\end{itemize}

% \subsection{Youtube-DLP Packgae (ELisp)} \hfill \\
% \begin{itemize}
	% \item Simple Emacs package that send commands to \emph{yt-dlp} python
	% 	package.
	% \end{itemize}

\subsection{Yee Light Package (ELisp)} \hfill \\
\begin{itemize}
	\item Simple Emacs package that send commands to \underline{\emph{\href{https://gitlab.com/stavros/yeecli/-/tree/master}{yeecli}}} python
		package.
\end{itemize}

\subsection{News Aggregator (Two Version: Python 3 \& Go)} \hfill \\
\begin{itemize}
	\item Created as Inoreader alternative for personal usage.
	\item Go version is the same as the Python 3 project but its written in Go
	for learning purpose.
	\item It's abonded due to only works on PC.
\end{itemize}


\subsection{Dotfiles Backupper (Python 3)} \hfill \\
\begin{itemize}
	\item Made for backing up \emph{Dotfiles} for both Windows and Linux.
	\item Used nearly for 2 years.
	\item Replaced with "\emph{git init --bare root}" method.
\end{itemize}

\newpage

\mylanguages{}
\mytechnicalskillsb{}
\mycertificates{}
% \myhobbiesb{}

\pagenumbering{gobble}
\end{document}
